---
title: "emission-data-package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{emission-data-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.dim = c(8, 6),
  fig.align = 'center',
  collapse = TRUE,
  comment = "#>"
)
```
This vignette summarizes the Lab 5 package and all its functions. To use the package, run the command below :
```{r setup}
library(advancedRLab5)
```

## get_figures()
The function `get_figures()` downloads emission data from kolada.se for
the municipality chosen by the user. The function argument `muni_name` is the name of the municipality
as a string. Here is an example how to use it:
```{r}
tail(get_figures("Linköping"))
```
The function returns a `data.frame` containing all the emission data. The
columns are:

* years <- the year in which the data has been gathered
* N00401 <- Total greenhouse gas emissions to air, tonnes of CO2 equivalents per capita
* N85078 <- Greenhouse gas emissions to air, agriculture, tonnes of CO2 equivalents per capita
* N85072 <- Greenhouse gas emissions to air, heating, tonnes of CO2 equivalents per capita
* N85075 <- Greenhouse gas emissions to air, machinery, tonnes of CO2 equivalents per capita
* N85077 <- Greenhouse gas emissions to air, industry, tonnes of CO2 equivalents per capita
* N85073 <- Greenhouse gas emissions to air, transport, tonnes of CO2 equivalents per capita
* N85076 <- Greenhouse gas emissions to air, electricity and district heating, tonnes of CO2 equivalents per capita

## plot_figures()
The function `plot_figures()` downloads emission data from kolada.se for the 
municipality chosen by the user and plots the graphs in different plots.
Here is an example how to use it:
```{r}
plot_figures("Linköping")
```
